### 2022-12-02 definitions.tex
details

We may generalyse thier result:

\begin{theorem}(ref)
{\sc resilience} is decidable for WSTS with strong upward compatibility and effective basis of $post^*$.
\end{theorem}

@@

@@

@@

\begin{proposition}
{\sc $k$-resilience}, hence {\sc bounded resilience} and {\sc resilience}, is undecidable for effective WSTS with strong upward compatibility ?
\end{proposition}

>>>>

We may generalyse thier result by weakiening the result

\begin{corollary}
{\sc resilience} is decidable for WSTS with strong upward compatibility and effective basis of $post^*$.
\end{corollary}

@@

\begin{theorem}(ref)
{\sc bounded resilience} is undecidable ??? for WSTS with upward compatibility and effective basis of $post^*$ ???
\end{theorem}

@@

\begin{proof}
on choisit $J=S$ ou $Reach(S)$. {$\forall s  \exists s'' \in I ~ s' \rightarrow^{\leq k} s''$ ?\newline}. il existe un chemin infini passant par inft par $q$, liveness undecidable LCS, Reset, WSTS.
\end{proof}

@@

\begin{proposition}
{\sc $k$-resilience}, hence {\sc bounded resilience} and {\sc resilience}, is undecidable for effective WSTS with strong upward compatibility ????
\end{proposition}
